Apparent preferences for cognitive effort fade when multiple forms of effort

### 2021-01-03 Cost_manuscript.Rmd
updated figs 5 through 8

```{r Survival and prepost plots (Fig. 5), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of times when participants quit a trial over time. Bottom: Proportion accepted in the second half as a function of first half acceptances (left). Dashed lines indicate the mean for each group. On the right, the proportion accepted over time per group. The order of blocks was repeated in the second half (indicated by the black dashed line)."}
# plots generated in 16.3.1. and 16.3.2.
(suppressWarnings(survPlot_btw) | RTplot_btw) / (prepost_btw$scatterplot | prepost_btw$propBlocks)
```

@@

``` {r BTW: 16.3.2. Plot Pre/Post reward x handling, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# this plot divides the proportion of acceptances for each reward/handling combination per half of the experiment
hrprepostPlot_btw <-dataBtw %>%
  group_by(SubjID) %>%
  mutate(Half = ifelse(Half == "Half_1", "First Half", "Second Half")) %>%
  group_by(SubjID, Half, Handling, Cost, Offer) %>%
  summarise(pAccept = mean(Choice)) %>%
  group_by(Half, Cost, Handling, Offer) %>%
  summarise(propAccept = mean(pAccept),
            SE = sd(pAccept) / sqrt(nSubjs_btw)) %>%
  ungroup() %>%
  mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
  ggplot(aes(Offer, propAccept, color = Cost)) +
    geom_point(size = 3, show.legend = T) +
    geom_line(size = 1, show.legend = F) +
    scale_color_manual(values = colsBtw) +
    scale_fill_manual(values = colsBtw) +
    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
    scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
    scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
    labs(y = "Proportion Accepted") +
    facet_wrap(vars(Handling, Half), ncol = 2) +
    theme(legend.position = "bottom",
          strip.text.x = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))

@@

```{r Prepost mixed effects plot (Fig. 6), eval = !figsEnd, fig.align = "center", fig.cap = "Distilling acceptance behavior before and after the break. Left: Proportion of acceptances per handling, reward, and half, showing that effortful demands became increasingly aversive over time. Right: Mixed-effects coefficients denoting the comparison among costs acceptances for each half separately (mirrored along the diagonal). Even though acceptances steadily decreased in the effort groups, the relative preferences were preserved."}
include_graphics("./Images/FIG6.png")

@@

# plot
earnFitplot_wth <- ggplot(data = temp, aes(pComplete, Earnings)) + 
         scale_color_manual(values = colsWth) + 
         geom_point(pch = 21, color = "black", size = 3, show.legend = T) + 
         stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
         labs(x = "Proportion Completed", y = "Total Earnings (dollars)") +
         scale_fill_manual(values = colsWth) +
         ylim(12, 16) +
         theme(panel.grid.major = element_blank(), 
           panel.grid.minor = element_blank(), 
           panel.background = element_blank(), 
           axis.line = element_line(colour = "black"),
           text = element_text(size = 16))

@@

# plot 
mixLogis_compare_wth$plot <- abicLogis_compare %>% 
  gather(Comparison, Value, AIC:BIC) %>%
  mutate(Model = factor(Model, levels = names(mixLogis_compare_wth))) %>%
  ggplot(aes(Model, Value, fill = Comparison)) +
    geom_point(color = "black", pch = 21, size = 3) +
    theme(legend.position = c(0.8, 0.8),
      legend.key = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_blank(),
      axis.line = element_line(colour = "black"),
      text = element_text(size = 16))

@@

```{r Earnings/prop completed/ME plots (Fig. 7), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "A: Quadratic relationship between trial completions and total earnings. B: proportion of acceptances of each reward per cost condition. C: Matrix of mixed-effects coefficients showing comparisons among costs (while controlling for reward amount). Comparisons between effort and wait trials from different blocks are omitted, as these are not considered in our original predictions. Crosses mark non-significant comparisons. D: AIC and BIC values for models of increasing complexity (a priori = AllMain)."}

@@

```{r Survival and prepost plots (Fig. 8), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of quitting times over time (right). Bottom: Proportion accepted in the second half as a function of first half acceptances (left). Dashed lines indicate the mean for each cost. On the right, the proportion accepted every time participants experienced a given block type."}
# plots generated in 16.3.1. and 16.3.3.
(suppressWarnings(survPlot_wth) | suppressWarnings(RTplot_wth)) / (prepost_wth$scatterplot | prepost_wth$propBlocks)
```

>>>>

```{r Survival and prepost plots (Fig. 5), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of times when participants quit a trial over time. Bottom: Proportion accepted in the second half as a function of first half acceptances (left). Dashed lines indicate the mean for each group. On the right, the proportion accepted over time per group. The order of blocks was repeated in the second half (indicated by the black dashed line)."}
# plots generated in 16.3.1. and 16.3.2.
# historyPlot_btw <- (suppressWarnings(survPlot_btw) | RTplot_btw) / (prepost_btw$scatterplot | prepost_btw$propBlocks)
# ggsave("./Images/FIG5_survival.png", historyPlot_btw, device = "png", height = 8, width = 10)
include_graphics("./Images/FIG5_survival.png")
```

@@

``` {r BTW: 16.3.2. Plot Pre/Post reward x handling, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# this plot divides the proportion of acceptances for each reward/handling combination per half of the experiment
hrprepostPlot_btw <-dataBtw %>%
  group_by(SubjID) %>%
  mutate(Half = ifelse(Half == "Half_1", "First Half", "Second Half")) %>%
  group_by(SubjID, Half, Handling, Cost, Offer) %>%
  summarise(pAccept = mean(Choice)) %>%
  group_by(Half, Cost, Handling, Offer) %>%
  summarise(propAccept = mean(pAccept),
            SE = sd(pAccept) / sqrt(nSubjs_btw)) %>%
  ungroup() %>%
  mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
  ggplot(aes(Offer, propAccept, color = Cost)) +
    geom_point(size = 3, show.legend = T) +
    geom_line(size = 1, show.legend = F) +
    scale_color_manual(values = colsBtw) +
    scale_fill_manual(values = colsBtw) +
    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 0.8, show.legend = T) +
    scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
    scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
    labs(y = "Proportion Accepted") +
    facet_wrap(vars(Handling, Half), ncol = 2) +
    theme(legend.position = "bottom",
          strip.text.x = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 28))

@@

```{r Prepost mixed effects plot (Fig. 6), eval = !figsEnd, fig.align = "center", fig.cap = "Distilling acceptance behavior before and after the break. Left: Proportion of acceptances per handling, reward, and half, showing that effortful demands became increasingly aversive over time. Right: Mixed-effects coefficients denoting the comparison among costs acceptances for each half separately (mirrored along the diagonal). Even though acceptances steadily decreased in the effort groups, the relative preferences were preserved."}
# left plot in 16.3.2
#ggsave("./Images/prepost_btw.png", hrprepostPlot_btw, device = "png", height = 6, width = 6)
include_graphics("./Images/FIG6_prepostbtw.png")

@@

# plot
earnFitplot_wth <- ggplot(data = temp, aes(pComplete, Earnings)) + 
         scale_color_manual(values = colsWth) + 
         geom_point(pch = 21, color = "black", size = 3, show.legend = T) + 
         stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
         labs(x = "Proportion Completed", y = "Total Earnings (dollars)") +
         scale_fill_manual(values = colsWth) +
         ylim(12, 16) +
         theme(panel.grid.major = element_blank(), 
           panel.grid.minor = element_blank(), 
           panel.background = element_blank(), 
           axis.line = element_line(colour = "black"),
           text = element_text(size = 22))

@@

# plot 
mixLogis_compare_wth$plot <- abicLogis_compare %>% 
  gather(Comparison, Value, AIC:BIC) %>%
  mutate(Model = factor(Model, levels = names(mixLogis_compare_wth))) %>%
  ggplot(aes(Model, Value, group = Comparison, fill = Comparison)) +
    labs(x = "", y = "") +
    geom_line(aes(color = Comparison)) +
    geom_point(color = "black", pch = 21, size = 3) +
    theme(legend.position = c(0.75, 0.7),
          legend.key = element_blank(),
          axis.text.x = element_text(angle = 30, hjust = 1),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          axis.line = element_line(colour = "black"),
          text = element_text(size = 22))

@@

```{r Earnings/prop completed/ME plots (Fig. 7), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "A: Quadratic relationship between trial completions and total earnings. B: proportion of acceptances of each reward per cost condition. C: Matrix of mixed-effects coefficients showing comparisons among costs (while controlling for reward amount). Comparisons between effort and wait trials from different blocks are omitted, as these are not considered in our original predictions. Crosses mark non-significant comparisons. D: AIC and BIC values for models of increasing complexity (a priori = AllMain)."}
# earnFitplot_wth, hrPlot_wth, mixLogis_compare_wth$plot
ggsave("./Images/aic_wth.png", mixLogis_compare_wth$plot, device = "png", height = 5, width = 5)
include_graphics("./Images/FIG7_wthlogistic.png")
```

@@

```{r Survival and prepost plots (Fig. 8), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Top: Survival curve (left), and distribution of quitting times over time (right). Bottom: Proportion accepted in the second half as a function of first half acceptances (left). Dashed lines indicate the mean for each cost. On the right, the proportion accepted every time participants experienced a given block type."}
# plots generated in 16.3.1. and 16.3.3.
historyPlot_wth <- (suppressWarnings(survPlot_wth) | suppressWarnings(RTplot_wth)) / (prepost_wth$scatterplot | prepost_wth$propBlocks)
ggsave("./Images/FIG8_survival.png", historyPlot_wth, device = "png", height = 8, width = 10)
```
